### 2020-01-30 wuhan.tex
after meeting with Daniel

We draw 100,000 random samples from the probability distributions that represent the estimates of $\mathcal R_0$ and the assumed values of $\bar G$ and $\kappa$
and calculate the exponential growth rate $r$ via the inverse of \eref{gamma}:
\begin{equation}
r_i = \frac{{\mathcal R_{0i}}^{\kappa_i} - 1}{\kappa_i \bar{G}_i}.
\end{equation}
This allows us to approximate the probability distributions of the estimated exponential growth rates by each study.

@@

\jd{Fix exponential?}
We construct pooled estimates for each parameter ($r$, $\bar G$, and $\kappa$) using a Bayesian multilevel modeling approach, which assumes that the parameters across different studies come from the same Gamma distribution:
\begin{equation}
\begin{aligned}
r_i &\sim \mathrm{Gamma}(\mathrm{mean}=\mu_r, \mathrm{shape}=\alpha_r),\\
\bar{G}_i &\sim \mathrm{Gamma}(\mathrm{mean}=\mu_G, \mathrm{shape}=\alpha_G),\\
\kappa_i &\sim \mathrm{Exponential}(\mathrm{mean}=\mu_\kappa),\\
\end{aligned}
\end{equation}
We account for uncertainties associated with $r_i$, $\bar G_i$ and $\kappa_i$ (and their correlations), by drawing random samples at each Metropolis-Hastings step from 100,000 samples that we calculated earlier;
this approach is analogous to Bayesian methods for analyzing phylogenetic data, which pften rely on drawing random samples of phylogenetic trees from a discrete set to account for phylogenetic uncertainty \citep{pagel2004bayesian,bedford2014integrating}.
\jd{use mean (not rate) and shape; specify units for the means. Use this as an opportunity to question your choices maybe. Consider using 1 week and 1/week for the means.}
Weak priors are assumed on the hyperparameters:
\begin{equation}
(\mu_r, \alpha_r, \mu_G, \alpha_G, \mu_\kappa) \sim \mathrm{Gamma}(\mathrm{shape}=0.1, \mathrm{rate}=0.1).
\end{equation}
We run 4 parallel Markov Chain Monte Carlo (MCMC) chains that consist of 200,000 burnin steps and 200,000 sampling steps.
Posterior samples are thinned every 400 steps.
Convergence is assessed by ensuring that the Gelman-Rubin statistic is below 1.01 for all parameters \citep{gelman1992inference}.

>>>>

For each study, we construct a family of parameter sets by drawing 100,000 random samples from the probability distributions that represent the estimates of $\mathcal R_0$ and the assumed values of $\bar G$ and $\kappa$
and calculating the exponential growth rate $r$ via the inverse of \eref{gamma}:
\begin{equation}
r_i = \frac{{\mathcal R_{0i}}^{\kappa_i} - 1}{\kappa_i \bar{G}_i}.
\end{equation}
This allows us to approximate the probability distributions of the estimated exponential growth rates by each study.

@@

\jd{Fix exponential?}
We construct pooled estimates for each parameter ($r$, $\bar G$, and $\kappa$) using a Bayesian multilevel modeling approach, which assumes that the parameters across different studies come from the same Gamma distribution:
\begin{equation}
\begin{aligned}
r_i &\sim \mathrm{Gamma}(\mathrm{mean}=\mu_r, \mathrm{shape}=\alpha_r),\\
\bar{G}_i &\sim \mathrm{Gamma}(\mathrm{mean}=\mu_G, \mathrm{shape}=\alpha_G),\\
\kappa_i &\sim \mathrm{Exponential}(\mathrm{mean}=\mu_\kappa),\\
\end{aligned}
\end{equation}
We account for uncertainties associated with $r_i$, $\bar G_i$ and $\kappa_i$ (and their correlations), by drawing a random set from the family of parameter sets for each study at each Metropolis-Hastings step;
this approach is analogous to Bayesian methods for analyzing phylogenetic data, which often rely on drawing random samples of phylogenetic trees from a discrete set to account for phylogenetic uncertainty \citep{pagel2004bayesian,bedford2014integrating}.
\jd{use mean (not rate) and shape; specify units for the means. Use this as an opportunity to question your choices maybe. Consider using 1 week and 1/week for the means.}
Weak priors are assumed on the hyperparameters:
\begin{equation}
(\mu_r, \alpha_r, \mu_G, \alpha_G, \mu_\kappa) \sim \mathrm{Gamma}(\mathrm{shape}=0.1, \mathrm{rate}=0.1).
\end{equation}
We run 4 parallel Markov Chain Monte Carlo (MCMC) chains that consist of 200,000 burnin steps and 200,000 sampling steps.
Posterior samples are thinned every 400 steps.
Convergence is assessed by ensuring that the Gelman-Rubin statistic is below 1.01 for all parameters \citep{gelman1992inference}.
